Specialisation in food webs scales with species richness but not with latitude

### 2015-08-28 manuscript/latitudepaper.tex
Removed fancy citations for Vancouver style

% let's get some nature formatted citations
%\usepackage{overcite}
\usepackage[round]{natbib}

@@

  Food webs --networks of feeding links between species-- have been used for
  several decades to summarise the structure of  ecological
  communities~\citep{Paine1966,Williams2000,Petchey2008} and to understand how
  that structure relates to environmental variables  such as habitat
  type~\citep{Briand1983,Shurin2006}, primary
  productivity~\citep{Townsend1998,Thompson2005a,Vermaat2009}, and
  climate~\citep{Petchey2010,Baiser2012}. The latter variables in turn have
  strong gradients over latitude, with productivity and temperature both being
  higher in the tropics while  climate is more variable at high
  latitudes~\citep{Field1998}. These variables affect both the resources
  available and species'
  metabolisms~\citep{White2007,OConnor2009,Hechinger2011,White2011}, and have
  been proposed as determinants of the strength of  interspecific
  interactions~\citep{Schemske2009,Lang2012,Schleuning2012}.  By modulating
  interactions between species, latitudinal gradients may also shape food-web
  structure. Indeed, these latitudinal environmental gradients have been put
  forward as potential drivers for the  latitudinal gradient in species
  richness, one of the most general and robust patterns in
  ecology~\citep{Kaufman1995,Macpherson2002,Schemske2009}.

  % These gradients, together with the strength and generality of associations between biological processes and environmental variables, suggest that variation in network structure 
  % may also be explained by ecological gradients \citep{Baiser2012}.

  One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\citep{Vazquez2004}. 
  This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
  turn should evolve smaller niches~\citep{Vazquez2004}. These narrow niches should therefore allow more species to 
  coexist in the tropics than at higher latitudes. Alternatively, the higher productivity of the tropics~\citep{Brown2004}
  may result in a broader niche space~\citep{Davies2007} which could also sustain greater biodiversity even if niche 
  sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocally 
  supported~\citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
  richness~\citep{Lappalainen2006,Krasnov2008,Slove2010}.

  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\citealp{Elton1927,Leibold2010}) of species within food webs.
  Specifically, narrower niches in the tropics would equate to
  greater specialisation (narrower niches) while constant niche sizes but
  greater productivity would translate to constant specialisation and niche
  width across latitude.
  Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
  For example,
  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics (\citealp{Marra1997,Dyer2007};
  but see~\citealp{Schleuning2012}). However,
  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness.

@@

    We compiled a list of 166 empirical food webs from
    multiple sources (see \emph{Appendix S1} for web origins and selection
    criteria). We recorded study site latitude from the original source where
    possible or, where study sites were described but exact coordinates were not
    given, obtained estimated coordinates using Google Earth~\citep{GoogleEarth}.
    We then divided the species in each web into basal resources (those species with
    consumers but no prey), top predators (those species with prey but no predators),
    and intermediate consumers (species with both predators and prey, including cannibalistic
    species). We grouped food web by ecosystem type (stream, N=71; lake, N=47; marine, 
    N=28; estuarine, N=18; and terrestrial, N=31) according to their designation in 
    previous aggregations of food webs (i.e.,~\citet{GlobalWeb,Riede2011,Dunne2013}).

    As the food webs in this dataset are derived from a variety of sources and were compiled over many decades, it
    is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
    Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
    sets to form ``trophic species'' webs ~\citep{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
    is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
    species with identical sets of interactions. We therefore analysed both original (i.e., without aggregating 
    any species) and trophic-species (i.e., after aggregating species with identical predators and prey) versions
    of the dataset; in each case using the number of species and 
    feeding links in each web to calculate the mean link density (number of links per species), mean generality 
    (number of prey per species), and mean vulnerability (number of predators per species) of the web. 
    The version of the dataset used did not qualitatively change the results, suggesting that
    the scaling relationships between species richness, other food-web properties, and latitude are very 
    similar whether or not redundant species are included. For simplicity, here we present only
    the results for the original (un-aggregated) webs.

@@

    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
    marine, lake, and terrestrial networks with estuarine
    networks providing the intercept) and $\epsilon_{i}$ is a residual error term. 
    We next calculated the AIC
    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
    using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
    Simplified models were obtained by
    systematically removing all possible combinations of terms from the full model.
    The best-fitting model was then determined to be the model with the fewest terms 
    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
    model.

@@

    The scaling relationship between link density ($Z$) and species richness ($S$)
    has been shown to be a power law~\citep{Riede2010} of the form

@@

    \noindent As the two forms imply a statistical fit to the data to different error 
    distributions, neither of which has strong
    \emph{a priori} justification in our dataset, we followed the recommendations in~\citet{Xiao2011}
    to compare the two model formulations explicitly (see \emph{Appendix S2} for details). 
    The logarithmic form (equation~\ref{Loglog}) provided the better fit to the data,
    as did the logarithmic forms of similar models for the scaling of generality and vulnerability. 
    We therefore used and present logarithmic models throughout the rest of the study.

@@

    We then simplified each model. To do this, we calculated the AIC of the
    maximal model as well as the AIC's of a suite of candidate simplified
    models identified using the R~\citep{R} function dredge from package
    MuMIn~\citep{MuMIn}.  Simplified models were obtained by systematically
    removing all possible combinations  of terms from the full model with the
    restriction that species richness was retained in all reduced models. The
    best-fitting model was then determined to be the model with the fewest
    terms  where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
    As a supplemental check to ensure that variation in sampling effor across
    food webs was not responsible for the trends we observed, we then repeated
    our analyses using jackknifed data sets in which we 1) sequentially removed
    each food web in the dataset and 2) sequentially removed sets of food webs 
    associated with each author of the food webs in the dataset. Parameter 
    estimates varied very little across either series of jackknifes (\emph{Appendix SXX}).
    % If several models shared the fewest
    % number of terms  and had $\Delta$AIC\textless2, the model with the lowest
    % AIC in that set was chosen as the best-fit model.

@@

  The tendency of food-web structure to exhibit scaling relationships with
  species richness has been well-established~\citep{Dunne2004,Riede2010}. As
  species richness in particular is also known to vary systematically over
  latitude~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009},
  intuitively one might suspect that any relationship between food-web
  properties such as generality might be due to the latitudinal gradient in
  species richness. In this dataset, however, we did not find overall
  latitudinal gradients in species richness, links per species,generality,
  vulnerability, or the proportions of food webs accounted for by basal
  resources, intermediate consumers, and top predators, except in lake and
  stream food webs where the proportions of top predators tended to decrease
  towards the poles  (see \emph{Appendix S3} for details).

  The lack of a latitudinal gradient in species richness in this dataset
  contrasts strongly with other
  studies~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. As
  numbers of species and links included in a food web vary strongly with
  sampling effort as well as with the underlying diversity of the study area,
  it is possible that the lack of latitudinal trends here is a result of
  researchers tending to expend similar amounts of sampling effort across
  studies. This could result in food webs describing species-rich tropical
  communities omitting more species and links than species-poor arctic
  communities. In addition, it is worth noting that gradients in species
  richness are generally measured for a single taxonomic group at a
  time~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. It is possible
  that these taxa are not well-represented in our food webs and that the
  dominant taxa in them do not have an underlying latitudinal gradient in
  richness.In either case, the lack of a strong association between species
  richness and latitude in any ecosystem type means that any effect of
  latitude on other scaling relationships is not being driven by an underlying
  latitudinal gradient in species richness. The lack of confounding effects of
  latitude allows us to more clearly assess effects of latitude on scaling
  with species richness and proportions of species in different trophic
  levels.

  Scaling of links per species, generality, and vulnerability with species
  richness varied strongly across ecosystem types. In estuarine, marine, and
  terrestrial food webs scaling of each property varied little with latitude.
  This is consistent with the idea that species' niche breadths do not vary
  systematically with temperature and productivity but that the niche space
  might be larger in species-rich communities~\citep{Davies2007}. Rather than
  niche space depending on temperature and productivity, it may be that species
  diversity itself affects the niche space available to species (although climate
  may affect speciation rates and therefore the diversity in a region~\citep{Currie2004}). 
  For example, as the plant diversity of a community increases both the 
  variety of food available to herbivores and the structural variety of the habitat will also increase.

  Unlike other ecosystem types, the scaling of generality in lake and stream
  food webs was stronger (i.e.,generality increased more steeply with
  increasing species richness) in higher-latitude food webs. In lake food webs,
  this trend was echoed in the scaling relationships between species richness
  and links per species and vulnerability. This means that species in tropical
  freshwater communities gain fewer additional feeding links per additional
  species in the web and that species in tropical lakes also gain fewer
  predators, and fewer links in general, per additional species than species
  in high-latitude lakes. These trends are consistent with the hypothesis that
  greater stability in the tropics leads to narrower niches~\citep{Vazquez2004}
  and a higher proportion of specialists. This may be partly due to high-latitude 
  species tending to switch between different seasonally-available 
  prey~\citep{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
  freshwater ecosystems may have more stable composition.

  The scaling of link density, generality and vulnerability with proportions
  of species at different trophic levels, however, did not differ between
  lakes and most other food webs. Indeed, there was comparatively little
  variation in scaling with the trophic-level breakdown of a web across
  ecosystem types. Nevertheless, the negative relationships between the
  proportion of top predators in a web and link density and vulnerability were
  weaker (i.e., the scaling exponent was more strongly negative) in low-latitude 
  stream ecosystems. This may imply that top predators in high-latitude 
  streams tend to be more generalist than their low-latitude
  equivalents~\citep{Winemiller2008}, perhaps due to prey-switching during
  seasonal food shortages~\citep{Magalhaes1993}. More generally, the lack of
  correspondence between the scaling of food-web properties with species
  richness and with proportions of species at each trophic level suggests that
  the size and trophic breakdowns of a community can each provide different
  information~\citep{Downing2002}.

@@

  Overall, our results were inconsistent with the latitude-niche breadth
  hypothesis in estuarine, marine, and terrestrial communities but consistent
  with the hypothesis of greater specialisation in the tropics in stream and
  lake food webs. This suggests that different mechanisms may structure food
  webs in different habitat types and that freshwater food webs in particular
  may be strongly affected by seasonal variation. In addition, different
  relationships between latitude and niche breadth in different habitat types
  goes some way towards explaining the equivocal support for the opposing
  hypotheses of narrower niches in the tropics~\citep{Vazquez2004} and broader
  niche space in the tropics~\citep{Davies2007}; both have merit but appear to
  apply to different systems.

@@

  Food webs used in this study were retrieved from the University of Canberra's 
  GlobalWeb database (\citealp{GlobalWeb}; \emph{www.globalwebdb.com}) and from
  two papers (\citealp{Riede2011}; \emph{http://dx.doi.org/10.1111/j.1461-0248.2010.01568.x}
  and \citealp{Dunne2013}; \emph{http://dx.doi.org/10.1371/journal.pbio.1001579}). Original sources for the
  food webs are given in \emph{Appendix S1}.

@@

[[Need to find a spot to refer to the conceptual figure]]
\begin{figure}[h]
\centerline{\includegraphics*[width=.85\textwidth]{Figures/Other/conceptual_figure.eps}}
\caption{In A) we show the known scaling relationship between link density (links per species, L/S) and 
species richness. This scaling relationship is a power law and therefore linear in a log-log plot.
In B) we show two versions of the latitudinal-niche breadth hypothesis that have been proposed to
explain this gradient. Hypothesis 1 posits that greater environmental stability in the tropics will 
allow species to evolve narrower niches (indicated by the grey trapezoid). Hypothesis 2 suggests that species
will have constant niche sizes over latitude (indicated by the grey rectangle) but that
greater primary productivity in the tropics creates a larger niche space (indicated by the 
white trapezoid) such that each species still occupies a smaller proportion of the total niche
space. These two hypotheses have different implications for the scaling of food-web properties
such as the number of feeding links per species (L/S) with species richness. C) If hypothesis 1 is 
true, then the exponent of the scaling relationship between link density and species richness should 
be larger towards the poles, where each additional species in the food-web will have a larger niche 
(i.e., more feeding links). If hypothesis 2 is true, then the exponent of this
distribution should not vary significantly over latitude.}
\label{concept}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to the species richness of a food web. Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by species richness raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were used as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=166 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S1}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=166 empirical food webs.
Latitude is given in degrees from the equator regardless of direction. The
behaviour of exponents for the scaling of generality and vulnerability with
species richness was very  similar to those for link density, except for the
scaling of generality in streams where  the size of the exponent increased
towards the poles. See Fig.~\emph{S2, Appendix 5} for  all scaling
relationships.} \label{S} \end{figure}

>>>>

% let's get some nature formatted citations
%\usepackage{overcite}
% \usepackage[round]{natbib}

@@

  Food webs --networks of feeding links between species-- have been used for
  several decades to summarise the structure of  ecological
  communities~\cite{Paine1966,Williams2000,Petchey2008} and to understand how
  that structure relates to environmental variables  such as habitat
  type~\cite{Briand1983,Shurin2006}, primary
  productivity~\cite{Townsend1998,Thompson2005a,Vermaat2009}, and
  climate~\cite{Petchey2010,Baiser2012}. The latter variables in turn have
  strong gradients over latitude, with productivity and temperature both being
  higher in the tropics while  climate is more variable at high
  latitudes~\cite{Field1998}. These variables affect both the resources
  available and species'
  metabolisms~\cite{White2007,OConnor2009,Hechinger2011,White2011}, and have
  been proposed as determinants of the strength of  interspecific
  interactions~\cite{Schemske2009,Lang2012,Schleuning2012}.  By modulating
  interactions between species, latitudinal gradients may also shape food-web
  structure. Indeed, these latitudinal environmental gradients have been put
  forward as potential drivers for the  latitudinal gradient in species
  richness, one of the most general and robust patterns in
  ecology~\cite{Kaufman1995,Macpherson2002,Schemske2009}.

  % These gradients, together with the strength and generality of associations between biological processes and environmental variables, suggest that variation in network structure 
  % may also be explained by ecological gradients \cite{Baiser2012}.

  One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\cite{Vazquez2004}. 
  This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
  turn should evolve smaller niches~\cite{Vazquez2004}. These narrow niches should therefore allow more species to 
  coexist in the tropics than at higher latitudes. Alternatively, the higher productivity of the tropics~\cite{Brown2004}
  may result in a broader niche space~\cite{Davies2007} which could also sustain greater biodiversity even if niche 
  sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocally 
  supported~\cite{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
  richness~\cite{Lappalainen2006,Krasnov2008,Slove2010}.

  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\cite{Elton1927,Leibold2010}) of species within food webs.
  Specifically, narrower niches in the tropics would equate to
  greater specialisation (narrower niches) while constant niche sizes but
  greater productivity would translate to constant specialisation and niche
  width across latitude.
  Attempts to unravel these effects, however,
  are complicated by known relationships between species richness and many other network properties~\cite{Riede2010}. 
  For example,
  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics (\cite{Marra1997,Dyer2007};
  but see~\cite{Schleuning2012}). However,
  average numbers of links per species tend to increase in larger food webs~\cite{Dunne2006,Riede2010}. This means
  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness.

@@

    We compiled a list of 166 empirical food webs from
    multiple sources (see \emph{Appendix S1} for web origins and selection
    criteria). We recorded study site latitude from the original source where
    possible or, where study sites were described but exact coordinates were not
    given, obtained estimated coordinates using Google Earth~\cite{GoogleEarth}.
    We then divided the species in each web into basal resources (those species with
    consumers but no prey), top predators (those species with prey but no predators),
    and intermediate consumers (species with both predators and prey, including cannibalistic
    species). We grouped food web by ecosystem type (stream, N=71; lake, N=47; marine, 
    N=28; estuarine, N=18; and terrestrial, N=31) according to their designation in 
    previous aggregations of food webs (i.e.,~\cite{GlobalWeb,Riede2011,Dunne2013}).

    As the food webs in this dataset are derived from a variety of sources and were compiled over many decades, it
    is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
    Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
    sets to form ``trophic species'' webs ~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
    is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
    species with identical sets of interactions. We therefore analysed both original (i.e., without aggregating 
    any species) and trophic-species (i.e., after aggregating species with identical predators and prey) versions
    of the dataset; in each case using the number of species and 
    feeding links in each web to calculate the mean link density (number of links per species), mean generality 
    (number of prey per species), and mean vulnerability (number of predators per species) of the web. 
    The version of the dataset used did not qualitatively change the results, suggesting that
    the scaling relationships between species richness, other food-web properties, and latitude are very 
    similar whether or not redundant species are included. For simplicity, here we present only
    the results for the original (un-aggregated) webs.

@@

    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
    marine, lake, and terrestrial networks with estuarine
    networks providing the intercept) and $\epsilon_{i}$ is a residual error term. 
    We next calculated the AIC
    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
    using the R~\cite{R} function dredge from package MuMIn~\cite{MuMIn}. 
    Simplified models were obtained by
    systematically removing all possible combinations of terms from the full model.
    The best-fitting model was then determined to be the model with the fewest terms 
    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
    model.

@@

    The scaling relationship between link density ($Z$) and species richness ($S$)
    has been shown to be a power law~\cite{Riede2010} of the form

@@

    \noindent As the two forms imply a statistical fit to the data to different error 
    distributions, neither of which has strong
    \emph{a priori} justification in our dataset, we followed the recommendations in~\cite{Xiao2011}
    to compare the two model formulations explicitly (see \emph{Appendix S2} for details). 
    The logarithmic form (equation~\ref{Loglog}) provided the better fit to the data,
    as did the logarithmic forms of similar models for the scaling of generality and vulnerability. 
    We therefore used and present logarithmic models throughout the rest of the study.

@@

    We then simplified each model. To do this, we calculated the AIC of the
    maximal model as well as the AIC's of a suite of candidate simplified
    models identified using the R~\cite{R} function dredge from package
    MuMIn~\cite{MuMIn}.  Simplified models were obtained by systematically
    removing all possible combinations  of terms from the full model with the
    restriction that species richness was retained in all reduced models. The
    best-fitting model was then determined to be the model with the fewest
    terms  where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
    As a supplemental check to ensure that variation in sampling effor across
    food webs was not responsible for the trends we observed, we then repeated
    our analyses using jackknifed data sets in which we 1) sequentially removed
    each food web in the dataset and 2) sequentially removed sets of food webs 
    associated with each author of the food webs in the dataset. Parameter 
    estimates varied very little across either series of jackknifes (\emph{Appendix SXX}).
    % If several models shared the fewest
    % number of terms  and had $\Delta$AIC\textless2, the model with the lowest
    % AIC in that set was chosen as the best-fit model.

@@

  The tendency of food-web structure to exhibit scaling relationships with
  species richness has been well-established~\cite{Dunne2004,Riede2010}. As
  species richness in particular is also known to vary systematically over
  latitude~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009},
  intuitively one might suspect that any relationship between food-web
  properties such as generality might be due to the latitudinal gradient in
  species richness. In this dataset, however, we did not find overall
  latitudinal gradients in species richness, links per species,generality,
  vulnerability, or the proportions of food webs accounted for by basal
  resources, intermediate consumers, and top predators, except in lake and
  stream food webs where the proportions of top predators tended to decrease
  towards the poles  (see \emph{Appendix S3} for details).

  The lack of a latitudinal gradient in species richness in this dataset
  contrasts strongly with other
  studies~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. As
  numbers of species and links included in a food web vary strongly with
  sampling effort as well as with the underlying diversity of the study area,
  it is possible that the lack of latitudinal trends here is a result of
  researchers tending to expend similar amounts of sampling effort across
  studies. This could result in food webs describing species-rich tropical
  communities omitting more species and links than species-poor arctic
  communities. In addition, it is worth noting that gradients in species
  richness are generally measured for a single taxonomic group at a
  time~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. It is possible
  that these taxa are not well-represented in our food webs and that the
  dominant taxa in them do not have an underlying latitudinal gradient in
  richness.In either case, the lack of a strong association between species
  richness and latitude in any ecosystem type means that any effect of
  latitude on other scaling relationships is not being driven by an underlying
  latitudinal gradient in species richness. The lack of confounding effects of
  latitude allows us to more clearly assess effects of latitude on scaling
  with species richness and proportions of species in different trophic
  levels.

  Scaling of links per species, generality, and vulnerability with species
  richness varied strongly across ecosystem types. In estuarine, marine, and
  terrestrial food webs scaling of each property varied little with latitude.
  This is consistent with the idea that species' niche breadths do not vary
  systematically with temperature and productivity but that the niche space
  might be larger in species-rich communities~\cite{Davies2007}. Rather than
  niche space depending on temperature and productivity, it may be that species
  diversity itself affects the niche space available to species (although climate
  may affect speciation rates and therefore the diversity in a region~\cite{Currie2004}). 
  For example, as the plant diversity of a community increases both the 
  variety of food available to herbivores and the structural variety of the habitat will also increase.

  Unlike other ecosystem types, the scaling of generality in lake and stream
  food webs was stronger (i.e.,generality increased more steeply with
  increasing species richness) in higher-latitude food webs. In lake food webs,
  this trend was echoed in the scaling relationships between species richness
  and links per species and vulnerability. This means that species in tropical
  freshwater communities gain fewer additional feeding links per additional
  species in the web and that species in tropical lakes also gain fewer
  predators, and fewer links in general, per additional species than species
  in high-latitude lakes. These trends are consistent with the hypothesis that
  greater stability in the tropics leads to narrower niches~\cite{Vazquez2004}
  and a higher proportion of specialists. This may be partly due to high-latitude 
  species tending to switch between different seasonally-available 
  prey~\cite{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
  freshwater ecosystems may have more stable composition.

  The scaling of link density, generality and vulnerability with proportions
  of species at different trophic levels, however, did not differ between
  lakes and most other food webs. Indeed, there was comparatively little
  variation in scaling with the trophic-level breakdown of a web across
  ecosystem types. Nevertheless, the negative relationships between the
  proportion of top predators in a web and link density and vulnerability were
  weaker (i.e., the scaling exponent was more strongly negative) in low-latitude 
  stream ecosystems. This may imply that top predators in high-latitude 
  streams tend to be more generalist than their low-latitude
  equivalents~\cite{Winemiller2008}, perhaps due to prey-switching during
  seasonal food shortages~\cite{Magalhaes1993}. More generally, the lack of
  correspondence between the scaling of food-web properties with species
  richness and with proportions of species at each trophic level suggests that
  the size and trophic breakdowns of a community can each provide different
  information~\cite{Downing2002}.

@@

  Overall, our results were inconsistent with the latitude-niche breadth
  hypothesis in estuarine, marine, and terrestrial communities but consistent
  with the hypothesis of greater specialisation in the tropics in stream and
  lake food webs. This suggests that different mechanisms may structure food
  webs in different habitat types and that freshwater food webs in particular
  may be strongly affected by seasonal variation. In addition, different
  relationships between latitude and niche breadth in different habitat types
  goes some way towards explaining the equivocal support for the opposing
  hypotheses of narrower niches in the tropics~\cite{Vazquez2004} and broader
  niche space in the tropics~\cite{Davies2007}; both have merit but appear to
  apply to different systems.

@@

  Food webs used in this study were retrieved from the University of Canberra's 
  GlobalWeb database (\cite{GlobalWeb}; \emph{www.globalwebdb.com}) and from
  two papers (\cite{Riede2011}; \emph{http://dx.doi.org/10.1111/j.1461-0248.2010.01568.x}
  and \cite{Dunne2013}; \emph{http://dx.doi.org/10.1371/journal.pbio.1001579}). Original sources for the
  food webs are given in \emph{Appendix S1}.

@@

[[Need to find a spot to refer to the conceptual figure]]
\begin{figure}[h]
\centerline{\includegraphics*[height=.5\textheight]{Figures/Other/conceptual_figure.eps}}
\caption{In A) we show the known scaling relationship between link density (links per species, L/S) and 
species richness. This scaling relationship is a power law and therefore linear in a log-log plot.
In B) we show two versions of the latitudinal-niche breadth hypothesis that have been proposed to
explain this gradient. Hypothesis 1 posits that greater environmental stability in the tropics will 
allow species to evolve narrower niches (indicated by the grey trapezoid). Hypothesis 2 suggests that species
will have constant niche sizes over latitude (indicated by the grey rectangle) but that
greater primary productivity in the tropics creates a larger niche space (indicated by the 
white trapezoid) such that each species still occupies a smaller proportion of the total niche
space. These two hypotheses have different implications for the scaling of food-web properties
such as the number of feeding links per species (L/S) with species richness. C) If hypothesis 1 is 
true, then the exponent of the scaling relationship between link density and species richness should 
be larger towards the poles, where each additional species in the food-web will have a larger niche 
(i.e., more feeding links). If hypothesis 2 is true, then the exponent of thisdistribution should not vary significantly over latitude.}
\label{concept}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to the species richness of a food web. Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by species richness raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were used as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=166 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S1}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=166 empirical food webs.
Latitude is given in degrees from the equator regardless of direction. The
behaviour of exponents for the scaling of generality and vulnerability with
species richness was very  similar to those for link density, except for the
scaling of generality in streams where  the size of the exponent increased
towards the poles. See Fig.~\emph{S2, Appendix 5} for  all scaling
relationships.} \label{S} \end{figure}
